---
title: "p8105_hw5_hq2182"
author: "Hanfei Qi"
date: "11/13/2020"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1

Read the data.
Create a city_state variable (e.g. “Baltimore, MD”).
Create a variable s.t. Closed w/o arrest = No arrest = "unsolved", while Close by arrest = solved


```{r, message = FALSE}
homicide_df = 
  read_csv("homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa, AL")
```

Creat a new dataframe to store #total cases and #unsolved cases.
```{r, message = FALSE}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Run `prop.test` for "Baltimore, MD";
Apply `broom::tidy` to the result and pull the estimated proportion and confidence intervals,
then save them in another dataframe.
```{r}
Baltimore_prop = 
  prop.test(
  aggregate_df %>% filter(city_state == "Baltimore, MD") %>% pull(hom_unsolved),  
  aggregate_df %>% filter(city_state == "Baltimore, MD") %>% pull(hom_total)) %>% 
  broom::tidy() %>% 
  select(estimate, conf.low, conf.high)
```

Run `prop.test` for each city and extract estimated proportion and confidence intervals.
```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

Create a plot that shows the estimates and CIs for each city, add error bars based on the upper and lower limits.
```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  ylab("Unsolved Homicides Proportion") +
  xlab("City, State") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```


# Problem 2

```{r}

```

